Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-03 src/paper.tex
update

Discretization methods have been studied for speech 
enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, 
however, this approach has 
been rarely studied for target speaker extraction. Our work focuses on utilizing discrete tokens 
to do target speaker extraction.

>>>>

Discretization methods have been studied for speech 
enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, 
however, this approach has 
been rarely studied for target speaker extraction. In this paper, we present a novel way to do 
target speaker extraction using discrete tokens and LMs. Inspired by the blind speech separation 
networks proposed in DASB \cite{dasb}, our model has three stages: encoding, modeling and decoding.
For the encoding stage.
